I can see clearly now: reinterpreting statistical significance

### 2018-05-04 doc.tex
Meeting with BB
Interrupted (working with BB earlier)

\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) have resulted in
calls to abandon its use. Alternatively, we argue that statistical hypothesis tests are useful, but are not, and should not
be referred to, as tests of significance. We propose a simple method to reduce misconceptions about NHST and p~values: 
refer to the results of NHST (i.e. $p <$ or $> 0.05$) using ``statistical clarity'' rather than ``statistical significance''. A test of the null hypothesis tells 
us whether or not we can \emph{clearly} see our effect (e.g. whether we can clearly see that a correlation is positive or 
negative, or if a response in the treatment group is greater than the response in the control group). Specifically, we argue 
that the use of ``statistical clarity'' will help researchers avoid accepting the null hypothesis and reclaim the English 
definition for ``significance'', allowing for a shift in focus to substantive significance.

@@

\textbf{Venue:} \mk{My list, no input from PIs on this yet}. No idea... Forum in Trends in E and E: max 1200 words?
Note in The American Naturalist: max 3000 words? Perspectives article in Nature?
Oikos forum? \url{http://www.oikosjournal.org/authors/author-guidelines}: ``Proposals should be no more than half a page in length and should include statements about the novelty and need for the piece as well as suggestions with regard to which members of the editorial board would be most suited to evaluating the proposal.''

>>>>

\textbf{Abstract}: Null hypothesis significance testing (NHST) remains popular despite decades of concern about misuse and misinterpretation.
Here we argue that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word commonly uis not about  whatever the use of have led to debates over whether to abandon its use. 
What to say about when and how they are useful? 
Conflation?
Get to the point!
Part of the problem here is the use of the word ``significance''. 
While hypothesis testing may be Here, we argue that statistical hypothesis tests are useful, but are not, and should not
be referred to, as tests of significance. We propose a simple method to reduce misconceptions about NHST and p~values: 
refer to the results of NHST (e.g. $p <$ or $> 0.05$) using ``statistical clarity'' rather than ``statistical significance''. 
A test of the null hypothesis tells 
us whether or not we can \emph{clearly} see our effect (e.g. whether we can clearly see that a correlation is positive or 
negative, or if a response in the treatment group is greater than the response in the control group). Specifically, we argue 
that the use of ``statistical clarity'' will help researchers avoid accepting the null hypothesis and reclaim the English 
definition for ``significance'', allowing for a shift in focus to substantive significance.

@@

\textbf{Venue:} Forum in Trends in E and E: max 1200 words?
Note in The American Naturalist: max 3000 words? Perspectives article in Nature?
Oikos forum? \url{http://www.oikosjournal.org/authors/author-guidelines}: ``Proposals should be no more than half a page in length and should include statements about the novelty and need for the piece as well as suggestions with regard to which members of the editorial board would be most suited to evaluating the proposal.''
